Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2016-07-15 draft.tex
reverse sections 2.2.1 and 2.2.2 to make payoffs to outside actors clear
add footnote about outside actors' payoffs in absorbing states

Player $p$'s payoffs in period $t$ are $U_p^t= -\alpha X+\lambda Y -R_p^t$, while the payoffs for player $c$ are $U_c^t= \beta X-\nu Y -R_c^t$, with both payoffs denoted in currency units. Taking $\alpha, \ \beta, \lambda,$ and $\nu$ to be positive, these payoffs represent the idea that the patron opposes reunification while player $c$ prefers it, and that the patron prefers recognized independence while player $c$ is averse to the creation of new states.

@@

>>>>

@@

Player $p$'s payoffs in period $t$ are $U_p^t= -\alpha X+\lambda Y -R_p^t$, while the payoffs for player $c$ are $U_c^t= \beta X-\nu Y -R_c^t$, with both payoffs denoted in currency units.\footnote{Note that, in equilibrium, after an absorbing state has been reached, neither outside player will make any investments. Thus the relevant per period payoff will be repeated with $R_p^i = R_c^i = 0$ for $i > t$ if an absorbing state is reached at time $t$.} Taking $\alpha, \ \beta, \lambda,$ and $\nu$ to be positive, these payoffs represent the idea that the patron opposes reunification while player $c$ prefers it, and that the patron prefers recognized independence while player $c$ is averse to the creation of new states.
